---
title: "R-eproducibility Assignment"
output: pdf_document
---
# Project Info
**January 26, 2022**  
**Diego Sancho Kruppa 20101377**   
**DSanchoKruppa on GitHub**  
**https://github.com/DSanchoKruppa/R-eproducibilityAssignment**  
  
This project demonstrates some basic data wrangling techniques using dplyr by manipulating 'FallopiaData.csv' and writing the data to a new file. Additionally, a custom function is defined and used to calculate descriptive statistics of the dataset. Finally, the entire project is linked to a public Git repository [**here**](https://github.com/DSanchoKruppa/R-eproducibilityAssignment) to demonstrate version control using Git.

___
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Set up
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
fDat <- read.csv("./InputData/FallopiaData.csv")
```

## Trimming data
```{r}
fDat <- fDat %>% 
  filter(Total > 60) %>% # removing entries with total < 60
  select(Total, Taxon, Scenario, Nutrients) %>% # reordering columns
  mutate(TotalG = Total * 0.001) %>% # converting Total from mg to g
  select(TotalG, Taxon, Scenario, Nutrients) # replacing Total with TotalG
```

## Defining a custom function  
```{r}
myFunc <- function(x, op) {
  if (op == "Average") {
    return(mean(x))
  }
  if (op == "Sum") {
    return(sum(x))
  }
  if (op == "Observations") {
    return(length(x))
  }
  else {
    message("Unknown string; try 'Average', 'Sum' or 'Observations'")
    stop()
  }
}
```

## Using the custom function  
```{r}
# Total number of observations in the 'Taxon' column
myFunc(fDat$Taxon, "Observations")

# Average TotalG for 'low' nutrient
lowDat <- fDat %>% 
  filter(Nutrients == "low")

myFunc(lowDat$TotalG, "Average")

# Average TotalG for 'high' nutrient
highDat <- fDat %>% 
  filter(Nutrients == "high")

myFunc(highDat$TotalG, "Average")
```

## Writing the wrangled data to a new .csv  
```{r}
write.csv(fDat, "./Output/WrangledData.csv")
```




